[dcpo_demsupport]

### 2020-09-03 paper/dcpo_demsupport.Rmd
loading data in the front
results with the trimmed data

df_controls <- read_csv(here::here("data", "control_variables.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1)

df_dcpoMeanAJPS <- df_dcpoMean %>% 
  left_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

@@

save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))
save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

@@

load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
load(here::here("output", "estimates_dcpo.RDS"))

@@

df_plot <- df_result_dcpoMean[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

@@

df_plot <- df_result_dcpoMean[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

>>>>

save(df_dcpoMean, file = here::here("output", "estimates_dcpoMean.RDS"))

df_controls <- read_csv(here::here("data", "control_variables_ajps.csv"),
                        col_types = cols(.default = col_double(),
                                         country = col_character(),
                                         country_name = col_character(),
                                         ISO = col_character(),
                                         Region_UN = col_character())) %>% 
  mutate(country0 = iconv(country, "latin1", "UTF-8", sub=''),
         country = countrycode::countrycode(country0, "country.name", "country.name"),
         regime = Vdem_regime > 1) %>% 
  filter(year >= first_year) # using trimmed data as Claassen

df_dcpoMeanAJPS <- df_dcpoMean %>% 
  right_join(df_controls, by = c("country", "year")) %>% 
  mutate(theta_dem = theta * regime,
         theta_aut = theta * (1 - regime)) %>% 
    plm::pdata.frame(index = c("country", "year"))

@@

save(df_result_dcpoMeanAJPS, file = here::here("output", "estimates_dcpoMeanAJPS.RDS"))
```

@@

df_result_dcpoAJPS <- map(mod_ls, estimate_dcpo)

save(df_result_dcpoAJPS, file = here::here("output", "estimates_dcpoAJPS.RDS"))
```

@@

load(here::here("output", "estimates_clsAJPS.RDS"))
load(here::here("output", "estimates_dcpoMeanAJPS.RDS"))
load(here::here("output", "estimates_dcpoAJPS.RDS"))

@@

df_plot <- df_result_dcpoMeanAJPS[[1]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)

@@

df_plot <- df_result_dcpoMeanAJPS[[2]] %>% 
  mutate(model = "DCPO\n (Point Estimates)") %>%  
  bind_rows(df_plot)
